Bring More Buses: Transit Delays in the Toronto Transit Commission

### 2024-02-01 outputs/paper/paper.qmd
fixed appendix and refs formatting based on rohan's comments.

Finally, the delays on particular subway lines and bus/streetcar routes were examined. Given the large number of different transit routes offered by the TTC, this analysis focuses on the 10 routes with the highest average delay times and highest incidence of delay. These findings are illustrated in @fig-highest-1 and @fig-highest-2. A short guide to the route number nomenclature of the TTC is provided in the Appendix for the reader's convenience.

@@

# Appendix 
Route nomenclature has gone through many changes throughout the history of the TTC. As James Bow, a TTC historian, said to BlogTO, "[The current system] is a kludge of several numbering schemes that were added to or replaced elements of the original scheme, with many elements grandfathered in". Hence, he says "there's very little rhyme or reason" to the transit numbering, making it confusing to almost everyone. [@flack]

>>>>

Finally, the delays on particular subway lines and bus/streetcar routes were examined. Given the large number of different transit routes offered by the TTC, this analysis focuses on the 10 routes with the highest average delay times and highest incidence of delay. These findings are illustrated in @fig-highest-1 and @fig-highest-2. A short guide to the route number nomenclature of the TTC is provided in the Appendix (@sec-appendix) for the reader's convenience.

@@

\newpage

::: {#refs}
:::

\newpage

# Appendix {#sec-appendix}

Route nomenclature has gone through many changes throughout the history of the TTC. As James Bow, a TTC historian, said to BlogTO, "[The current system] is a kludge of several numbering schemes that were added to or replaced elements of the original scheme, with many elements grandfathered in". Hence, he says "there's very little rhyme or reason" to the transit numbering, making it confusing to almost everyone. [@flack]
